---
title: "Replicated results"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
library(magrittr)

# An auxiliary function to get a targets object depending on `TAR_PROJECT`
read_target <- function(name_target, tar_project) {
  name_target <- as.character(substitute(name_target))
  withr::with_envvar(
    new = c("TAR_PROJECT" = tar_project),
    targets::tar_read_raw(name_target)
  )
}
```

This R Markdown demonstrates how to retrieve the replicated results from the `targets` pipeline.

Before running the code below, make sure you have completed `source("run.R")`.

If you have run the pipeline with dummy data, set the `R_CONFIG_ACTIVE` environment variable to `"dummy"`
Otherwise, leave `R_CONFIG_ACTIVE` unspecified or set it to `"default"`.

# Summary statistics

## Network statistics

```{r}
project_preprocess <- purrr::pluck(config::get(), "tar_projects", "preprocess")

graph_stats <- read_target(graph_stats, project_preprocess)

graph_stats$network_stats %>%
  dplyr::mutate(dplyr::across(c(k_core, n_nodes, edges, triangles), as.integer)) %>%
  modelsummary::datasummary_df()
```

### Degree

```{r}
as.list(graph_stats$degree_stats) %>%
  data.frame() %>%
  dplyr::rename(`1st.Qu.` = X1st.Qu., `3rd.Qu.` = X3rd.Qu.) %>%
  modelsummary::datasummary_df()
```

## Nodal characteristics

### Industry

```{r}
project_estimation <- purrr::pluck(config::get(), "tar_projects", "estimation")
read_target_est <- purrr::partial(read_target, tar_project = project_estimation)
```


```{r}
node_stats <- read_target_est(descriptive_stats)

node_stats$industry_counts %>%
  head(5) %>%
  dplyr::select(large_category_en, industry_share) %>%
  dplyr::mutate(industry_share = industry_share * 100) %>%
  dplyr::rename(Industry = large_category_en, `Share in the sample (%)` = industry_share) %>%
  modelsummary::datasummary_df(fmt = 1)
```


### Area

```{r}
node_stats$city_counts %>%
  dplyr::mutate(share = 100 * city_count / sum(city_count)) %>%
  head(5) %>%
  dplyr::summarise(share = sum(share)) %>%
  dplyr::mutate(area = "Minato-ku, Chiyoda-ku, Shibuya-ku, CHuo-ku, Shinjuku-ku") %>%
  dplyr::select(area, share) %>%
  dplyr::rename(Area = area, `Share in the sample (%)` = share) %>%
  modelsummary::datasummary_df(fmt = 1)
```

### Occupation

```{r}
node_stats$occupation_counts %>%
  head(2) %>%
  dplyr::mutate(Occupation = c("Sales-related positions", "Company directors")) %>%
  dplyr::select(Occupation, occupation_share) %>%
  dplyr::mutate(occupation_share = occupation_share * 100) %>%
  dplyr::rename(`Share in the sample (%)` = occupation_share) %>%
  modelsummary::datasummary_df(fmt = 1)
```


# Figure 2: Results of the Block Recovery Step

## (a) Lower Bound Convergence

```{r}
read_target_est(lower_bound_plot)
```

## (b) Block Size Distribution

```{r}
read_target_est(block_size_plot)
```

# Table 1: HERGM Parameter Estimates

```{r, results='asis'}
read_target_est(coefficients_table)
```

